---
title: "Does More (or Less) Crime Occur in Populous Areas?"
author: "Nikki"
date: "5/16/2020"
output: html_document
---

# A Simple Linear Regression Model to Determine the Relationship Between
# Population vs. Violent Crime

**Dataset Provided By:** [Kaggle](https://www.kaggle.com)

## Import the Required Libraries ##

```{r}

library(caTools)
library(ggplot2)

```

## Importing the Dataset ##

```{r}

dataset <- read.csv('crime_and_incarceration_by_state.csv')

na <- is.na(dataset$jurisdiction)

na

summary(dataset)

```

#### Splitting the Dataset into a Training Set and Test Set ####

```{r}

set.seed(123)

split <- sample.split(dataset$violent_crime_total,
                      SplitRatio = 2/3)

training_set <- subset(dataset, split == TRUE)

test_set <- subset(dataset, split == FALSE)

regressor <- lm(formula = violent_crime_total ~ state_population,
                data = training_set)

summary(regressor)

```

## Predicting Test Set Results ##

### Vector of Predictions

```{r}

y_pred <- predict(regressor, newdata = test_set)
y_pred

```


## Plotting: Visualizing Training Set Results ##

```{r}

ggplot() + 
    geom_point(aes(x = training_set$state_population,
                   y = training_set$violent_crime_total),
               color = 'orange') +
    geom_line(aes(x = training_set$state_population,
                  y = predict(regressor, newdata = training_set)),
              color = 'purple') +
    ggtitle('Population vs. Violent Crime (Training Set)') +
    xlab('State Population') +
    ylab('Violent Crime')

```


## Visualizing Test Set Results ##

```{r}

ggplot() +
    geom_point(aes(x = test_set$state_population,
                   y = test_set$violent_crime_total),
               color = 'green') +
    geom_line(aes(x = training_set$state_population,
                  y = predict(regressor, newdata = training_set)),
              color = 'purple') +
    ggtitle('Population vs. Violent Crime (Test Set)') +
    xlab('State Population') +
    ylab('Violent Crime')

```



